---
title: "Starting a notes section"
description: "Why this exists, what'll go here, and a demo."
date: 2026-06-24
categories: [meta]
---

I'm going to be using this space to write up things as I learn them. 
Hopefully that forces me to actually understand a method well enough 
to explain it, and it leaves a trail of what I've been working through.

One thing I've enjoyed learning at the start of BUDS is the importance of 
effective visualizations. We've been leaning a lot on Claus O. Wilke's 
*Fundamentals of Data Visualization* and, as he outlines, I'm trying my 
best to balance the art and science of it. Here's a few examples I find cool!

A very basic ggplot method to view MPG by the number of Cylinders:

```{r}
#| message: false
#| warning: false
library(tidyverse)
```

```{r}
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_boxplot()
```

Now *my* version: 

```{r}
ggplot(mtcars, aes(x = mpg, y = factor(cyl), fill = factor(cyl))) +
  geom_boxplot() +
  scale_fill_manual(values = unname(palette.colors(palette = "Okabe-Ito"))[2:4]) +
  scale_x_continuous(breaks = seq(10, 35, 5)) +
  coord_cartesian(xlim = c(10, 35)) +
  labs(title = "Number of Cylinders vs MPG",
       y = "Cylinders",
       x = "Fuel Efficiency (MPG)") +
  guides(fill = "none") +
  theme_bw(base_size = 14)
```

Slightly more attractive!